Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-06 paper/paper.tex
update the paper to re-organize, and include the intro sample and more illustrative problem formulation

\section{Introduction}
The introduction \dots

@@

\section{CDRP Model Decomposition and Clustering}
\subsection{Critical Data Routing Path Model}
\subsection{CDRP Model Clustering}

\section{CDRP Model Assembly}
\subsection{The Assembly Problem}
For a clear formulation, we define the input of a problem instance to have the following components:
\begin{itemize}
	\item $L$ class labels, denoted $\{l_j\}$
	\item $N$ subclasses in total \begin{itemize}
		\item $M$ target subclasses, denoted $\mathcal{A} = \{A_i\}$
		\item $N-M$ dummy subclasses (with irrelevant class labels), denoted $\bar{\mathcal{A}} = \{A_i\}$
	\end{itemize}
	\item $g(A_i) := l_j$ the partial map from $A_i$ to class label $l_j$
	\item $K$ classifiers, denoted $\mathcal{D} = \{d_j\}$
	\item $f(A_i, d_j) := 0, 1$ the classifier certificate that $A_i$ is classified positive in classifier $d_j$
	\item $score(d_j)$ the accuracy(?) of classifier $d_j$
	\item $k$ the maximum number of classifier to use
\end{itemize}

The solution to the instance should contain:
\begin{itemize}
	\item $D \subset \mathcal{D}$ a set of $m$ classifiers \textit{covering} all $M$ target subclasses s.t. $m < k$
	\item $score(D)$ the overall accuracy(?) of the classifier set
\end{itemize}

We define the concept of \textit{covering} as follows.
\begin{definition}
	A set of classifiers covers $M$ target subclasses iff. given any sample, the joint classifier can determine whether it \textit{solely} belongs to \begin{enumerate}
		\item a subset (with consistent labels) of the $M$ target subclasses, or,
		\item the rest dummy subclasses $\bar{\mathcal{A}}$.
	\end{enumerate}
\end{definition}

@@

\subsection{The Algorithm}

>>>>

\section{Introduction}
\label{sec:intro}
The introduction \dots

\begin{figure}[h]
    \centering
    \includegraphics[width=0.75\linewidth]{fig/formulation_example.png}
    \caption{An Example Assembly Problem}
    \label{fig:assemble-example-venn}
\end{figure}

Figure~\ref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
The original dataset contains 3 classes $A_1, A_2$, and $A_3$, and we are able to decompose each into some subclasses, e.g., $A_1$ is decomposed into two subclasses of samples $A_{11}$ and $A_{12}$.
There are 4 binary classifiers, each determines whether a sample belongs to the union of some subclasses marked with boxes, e.g., $d_1$ determines whether a sample belongs to the union of $\{A_{11}, A_{12}, A_{21}, A_{22}\}$.
We can use classifiers $d_1, d_2, d_3$ and set operations for the classification task:
\begin{itemize}
	\item $d_1 - (d_2 + d_3)$ determines samples belong to $A_1$;
	\item $d_1 \cdot d_2 + d_3$ determines samples belong to $A_2$;
	\item $d_2 - d_1$ determines samples belong to $A_3$.
\end{itemize}
For the partial classification task of class $A_3$, it suffices to use only $d_2$ and $d_4$ and their intersection $d_2 \cdot d_4$ to determine samples in $A_3$.

@@

\section{The General Assembly Framework}
\label{sec:assembly}
In this section, we give the general framework to assemble multiple classifiers into one that performs complex classification tasks.
The classification task only need to cover a given set of labels, and we do not need to distinguish the remaining dummy classes.
We also propose an heuristic search algorithm to find a feasible solution to the assembly problem.

We only consider the general case of such assembly in this section, while we specialize the assembly problem w.r.t. input composed of CDRP models in \cref{sec:cdrp}.
The assembly problem can be easily extended to general classifier input, but we only discuss the case for binary classifier input for simplicity.

\subsection{The Assembly Problem}
\label{sec:assemble-problem}
We first formulate the problem by defining the input of an assembly problem and the output it requires.

The input have the following components:
\begin{itemize}
	\item $L$ class labels, denoted $\{l_j\}$
	\item $N$ subclasses in total \begin{itemize}
		\item $M$ target subclasses, denoted $\mathcal{A} = \{A_i\}$
		\item $N-M$ dummy subclasses, denoted $\bar{\mathcal{A}} = \{A_i\}$
	\end{itemize}
	\item $g(A_i) := l_j$ the partial map from $A_i$ to class label $l_j$
	\item $K$ classifiers, denoted $\mathcal{D} = \{d_j\}$
	\item $f(A_i, d_j) := 0, 1$ the classifier certificate function that $A_i$ is classified positive in classifier $d_j$
	\item $score(d_j)$ the performance score of classifier $d_j$
	\item $k$ the maximum number of classifier to use
\end{itemize}

The original dataset consists of $L$ classes with different labels.
Some prior knowledge allows us to decompose the dataset into $N$ subclasses of samples.
A subclass is the unit sample group we will consider in the assembly problem, and for a subclass to be \textit{consistent}, we assume all samples in a subclass have the sample label given by the partial map $g$.
Since we are only interested in a subset of labels, we group all $M$ target subclasses having these labels into $\mathcal{A}$
The rest $N-M$ subclasses are dummy ones.

We are given $K$ binary classifiers with domains of the entire dataset.
All samples in a subclass $A_i$ should be assigned the same 0-1 label by a classifier $d_j$, which is determined by the certificate function $f$.
To extend the assembly problem to general classifier inputs, we only need to change the certificate function $f$ for classifiers to allow return values from a set of multiple symbols.
The cardinality of $f$'s range should be $n$ for an $n$-classifier assembly problem.
For example, a ternary classifier assembly problem needs the certificate function to produce three possible symbols, i.e., $|range(f)| = 3$.

For each classifier, we also know its performance score, which could be its accuracy, its model complexity, or both.
There is a constraint for a problem instance that we can only use up to $k$ classifiers to assemble the final classifier.

The solution to the problem instance should contain:
\begin{itemize}
	\item $D \subset \mathcal{D}$ a set of $m$ classifiers \textit{distinguishing} all $M$ target subclasses s.t. $m < k$
	\item $score(D)$ the overall performance of the classifier set
\end{itemize}

\todo{The overal performance score.}

We define the concept of \textit{distinguishing} as follows.
\begin{definition}
	A set of classifiers covers $M$ target subclasses iff. given any sample, the joint classifier can determine whether it \textit{solely} belongs to \begin{enumerate}
		\item a subset (with consistent labels) of the $M$ target subclasses, or,
		\item the rest dummy subclasses $\bar{\mathcal{A}}$.
	\end{enumerate}
\end{definition}
In other word, the classifier should uniquely determine whether a sample have which of the target labels or the dummy label.

@@

\subsection{The Algorithm}
\label{sec:assembly-algorithm}

\section{Model Assembly based on CDRP Decomposition and Clustering}
\label{sec:cdrp}
\subsection{Critical Data Routing Path Model}
\subsection{CDRP Model Clustering}
\subsection{CDRP Model Assembly}
